---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
if ("simpleexample" %in% installed.packages()) {
  remove.packages("simpleexample")
}
```

# dict

<!-- badges: start -->
<!-- badges: end -->

The goal of dict is to make it easy to create, modify, and use word-based 
dictionaries for analyzing natural language texts. In other words, this package
is designed to create sentiment-analysis like tools for measuring the extent to
which natural language reflects (positively and/or negatively) any user-defined 
dimension or topic (e.g., politics, sports, emotions, active, pass, 
medical, philosophical, etc.).

## Installation

You can install the released version of dict from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("dict")
```

You can install the developmernt version of dict from [Github](https://github.com) with:

``` r
remotes::install_github("mkearney/dict")
```

## Example

Create vectors of positively and negatively identifying words for a simple 
"valence" dimension.

```{r}
## load package
library(dict)

## vector of positive words
pos <- c("like", "love", "amazing", "excellent", "great", "fantastic",
  "incredible", "awesome", "best", "favorite", "fan", "fun", "enjoyed",
  "enjoyed", "good", "solid", "better", "soooo", "happy")

## vetor of negative words
neg <- c("hate", "loathe", "dislike", "awful", "horrible", "worst",
  "miserable", "ruin", "ruining", "destroy", "destroyed", "destroying",
  "pathetic", "hated", "hateful", "unhappy", "horrifies", "horrifying",
  "terrible")
```

## Create dictionaries

Create a dictionary using only positively-defining words:

```{r}
## create dictionary using only positive words
dict(pos)
```

Create a dictionary using both positvely and negatively associated words:

```{r}
## create dictionary using both positive and negative words
d <- dict(list(pos = pos, neg = neg))

## view up to n entries of dictionary
print(d, n = 30)
```

## Use word dictionary

Apply a dictionary to some example text:

```{r}
## example text
txt <- c("love amazing excellent good",
"hate loathe horrifies unhappy terrible",
"awesome best hateful hated worst")

## get estimate for each element of txt using pos/neg dictionary
d(txt)

## store estimates in a tibble
tibble::tibble(
  text = txt,
  sent = d(txt)
)
```

## Export dictionary via R package

Export word dictionaries as super fast packages using this wrapper around `usethis::create_package()`

```{r}
## create package path via temp directory
path_pkg <- file.path(tempdir(), "simpleexample")

## create R package featuring d
sh <- capture.output(
  suppressMessages(create_dict_pkg(d, path_pkg))
)

## test new package's score function on txt vector
simpleexample::score(txt)
```

Compare the speed of the default returned function (written in R) versus the optimized version in the standalone package (written in C)

```{r}
## compare speed
bm <- bench::mark(
  fun = d(txt),
  pkg = simpleexample::score_score(txt),
  relative = TRUE
)

## view results
bm

## view plot
ggplot2::autoplot(bm)
```

## TO DO

See [issues labelled enhancement](https://github.com/mkearney/dict/labels/enhancement).
